On consistency scores in text data with an implementation in R

### 2021-01-08 outputs/documents/paper_ngrams.Rmd
Add comments to function code chunks

```{r, eval=FALSE}
tokens_from_example <- 
  quanteda::tokens(body_of_text, remove_punct = TRUE, )
tokens_from_example <- 
  quanteda::tokens_tolower(tokens_from_example)
```

@@

```{r, eval=FALSE}
# Create ngrams from the tokens
toks_ngram <- 
  toks_ngram <- quanteda::tokens_ngrams(tokens_from_example, n = 5:3)

@@

# We only want the common ones, not every one.
all_tokens <-
  all_tokens %>%
  dplyr::group_by(tokens) %>%
  dplyr::count() %>%
  dplyr::filter(n > 1) %>%
  dplyr::ungroup()
```

@@

```{r, eval=FALSE}
# Create a tibble that has the first two words in one column then the third
all_tokens <-
  all_tokens %>%
  dplyr::mutate(tokens = stringr::str_replace_all(tokens, "_", " "),
                first_words = stringr::word(tokens, start = 1, end = -2),
                last_word = stringr::word(tokens, -1),
                tokens = stringr::str_replace_all(tokens, " ", "_"),
                first_words = stringr::str_replace_all(first_words, " ", "_")
  ) %>%
  dplyr::rename(last_word_expected = last_word) %>%
  dplyr::select(-n)
```

@@

```{r, eval=FALSE}
# Create tokens with errors
tokens_from_example_with_errors <- 
  quanteda::tokens(text_to_check, remove_punct = TRUE)
tokens_from_example_with_errors <- 
  quanteda::tokens_tolower(tokens_from_example_with_errors)

@@

all_tokens_with_errors <-
  all_tokens_with_errors %>%
  dplyr::mutate(tokens = stringr::str_replace_all(tokens, "_", " "),
                first_words = stringr::word(tokens, start = 1, end = -2),
                last_word = stringr::word(tokens, -1),
                tokens = stringr::str_replace_all(tokens, " ", "_"),
                first_words = stringr::str_replace_all(first_words, " ", "_"))
```

@@

```{r, eval=FALSE}
all_tokens_with_errors <-
  all_tokens_with_errors %>%
  dplyr::left_join(dplyr::select(consistency_dataset, -tokens), 
                   by = c("first_words"))
```

@@

```{r, eval=FALSE}
# Calculate the internal consistency score:
internal_consistency <-
  internal_consistency %>%
  dplyr::ungroup()%>%
  dplyr::filter(!is.na(as_expected)) %>%
  dplyr::count(as_expected) %>%
  dplyr::mutate(consistency = true_count/sum(n))
```

@@

```{r, eval=FALSE}
# Identify which words were unexpected
unexpected <-
  all_tokens_with_errors_only %>%
  dplyr::mutate(as_expected = last_word == last_word_expected) %>%
  dplyr::filter(as_expected == FALSE) %>%
  dplyr::select(-tokens)
```

>>>>

```{r, eval=FALSE}
make_internal_consistency_dataset <- function(body_of_text) {
  tokens_from_example <- 
    quanteda::tokens(body_of_text, remove_punct = TRUE)
  tokens_from_example <- 
    quanteda::tokens_tolower(tokens_from_example)

# Continuous code...
}
```

@@

```{r, eval=FALSE}
make_internal_consistency_dataset <- function(body_of_text) {
# ... Previous code

  # Create ngrams from the tokens
  toks_ngram <- 
    toks_ngram <- quanteda::tokens_ngrams(tokens_from_example, n = 5:3)

@@

  # We only want the common ones, not every one.
  all_tokens <-
    all_tokens %>%
    dplyr::group_by(tokens) %>%
    dplyr::count() %>%
    dplyr::filter(n > 1) %>%
    dplyr::ungroup()

# Continuous code...
}
```

@@

```{r, eval=FALSE}
make_internal_consistency_dataset <- function(body_of_text) {
# ... Previous code

  # Create a tibble that has the first two words in one column then the third
  all_tokens <-
    all_tokens %>%
    dplyr::mutate(tokens = stringr::str_replace_all(tokens, "_", " "),
                  first_words = stringr::word(tokens, start = 1, end = -2),
                  last_word = stringr::word(tokens, -1),
                  tokens = stringr::str_replace_all(tokens, " ", "_"),
                  first_words = stringr::str_replace_all(first_words, " ", "_")
    ) %>%
    dplyr::rename(last_word_expected = last_word) %>%
    dplyr::select(-n)
}
```

@@

```{r, eval=FALSE}
generate_internal_consistency_score<-function(text_to_check, consistency_dataset){
  # Create tokens with errors
  tokens_from_example_with_errors <- 
    quanteda::tokens(text_to_check, remove_punct = TRUE)
  tokens_from_example_with_errors <- 
    quanteda::tokens_tolower(tokens_from_example_with_errors)

@@

  all_tokens_with_errors <-
    all_tokens_with_errors %>%
    dplyr::mutate(tokens = stringr::str_replace_all(tokens, "_", " "),
                  first_words = stringr::word(tokens, start = 1, end = -2),
                  last_word = stringr::word(tokens, -1),
                  tokens = stringr::str_replace_all(tokens, " ", "_"),
                  first_words = stringr::str_replace_all(first_words, " ", "_"))

# Continuous code...
}
```

@@

```{r, eval=FALSE}
generate_internal_consistency_score<-function(text_to_check, consistency_dataset){
#... Previous code

all_tokens_with_errors <-
  all_tokens_with_errors %>%
  dplyr::left_join(dplyr::select(consistency_dataset, -tokens), 
                   by = c("first_words"))

# Continuous code...
}
```

@@

```{r, eval=FALSE}
generate_internal_consistency_score<-function(text_to_check, consistency_dataset){
#... Previous code

  # Calculate the internal consistency score:
  internal_consistency <-
    internal_consistency %>%
    dplyr::ungroup()%>%
    dplyr::filter(!is.na(as_expected)) %>%
    dplyr::count(as_expected) %>%
    dplyr::mutate(consistency = true_count/sum(n))

# Continuous code...
}
```

@@

```{r, eval=FALSE}
generate_internal_consistency_score<-function(text_to_check, consistency_dataset){
#... Previous code

# Identify which words were unexpected
unexpected <-
  all_tokens_with_errors_only %>%
  dplyr::mutate(as_expected = last_word == last_word_expected) %>%
  dplyr::filter(as_expected == FALSE) %>%
  dplyr::select(-tokens)
}
```
